R Notebook

### 2018-09-13 article_code.Rmd
re arranging

mvtnorm compute integral over Gaussian densities
```{r}
library(mvtnorm)
library(abind)
```

```{r}
e1<-e2<-e3<-e4<-d1<-d2<-d3<-matrix(0,nz,4)
e1[env_lat==1]=1
e2[env_lat==2]=1
e3[env_lat==3]=1
e4[env_lat==4]=1
d1[diag_lat==1]=1
d2[diag_lat==2]=1
d3[diag_lat==3]=1
e1[is.na(env_lat)]=e2[is.na(env_lat)]=e3[is.na(env_lat)]=e4[is.na(env_lat)]=NA
d1[is.na(diag_lat)]=d2[is.na(diag_lat)]=d3[is.na(diag_lat)]=NA
```
```{r}
pe1 = mean(e1,na.rm=TRUE)
pe2 = mean(e2,na.rm=TRUE)
pe3 = mean(e3,na.rm=TRUE)
pe4 = mean(e4,na.rm=TRUE)
c(pe1,pe2,pe3,pe4)
pd1=mean(d1,na.rm=TRUE)
pd2=mean(d2,na.rm=TRUE)
pd3=mean(d3,na.rm=TRUE)
c(pd1,pd2,pd3)
pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

@@

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)
pe1+pe2+pe3+pe4
```

@@

```
ok we also want to display an image with all the logs
we are doubling the wells for a better visualization
```{r}
im<-matrix(NA,100,91)
im[5,]<-env_lat[,1]
im[4,]<-env_lat[,1]
im[25,]<-env_lat[,2]
im[24,]<-env_lat[,2]
im[35,]<-env_lat[,3]
im[34,]<-env_lat[,3]
im[95,]<-env_lat[,4]
im[94,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
print image
```{r}
png(file="logslate.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
we also want to display the environment of depositions and the diagenesis
```{r}
im<-matrix(NA,100,91)
im[5,]<-diag_lat[,1]+4
im[4,]<-diag_lat[,1]+4
im[8,]<-env_lat[,1]
im[7,]<-env_lat[,1]
im[25,]<-diag_lat[,2]+4
im[24,]<-diag_lat[,2]+4
im[28,]<-env_lat[,2]
im[27,]<-env_lat[,2]
im[35,]<-diag_lat[,3]+4
im[34,]<-diag_lat[,3]+4
im[38,]<-env_lat[,3]
im[37,]<-env_lat[,3]
im[95,]<-diag_lat[,4]+4
im[94,]<-diag_lat[,4]+4
im[98,]<-env_lat[,4]
im[97,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
```{r}
png(file="logslatediag2.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),ylab="Vertical distance (m)",xlab = "Lateral distance (m)")
```

@@

```{r}
library(mvtnorm)
```
```{r}
source("co_sim_condi.R")
```

>>>>

mvtnorm compute integral over Gaussian densities
```{r}
library(mvtnorm)
library(abind)
```
Getting the facies logs and transforming them into indicator variables
```{r}
env_lat<-data.matrix(read.table("depo_latemar.txt"))
diag_lat<-data.matrix(read.table("diag_latemar.txt"))
nz=nrow(env_lat)
e1<-e2<-e3<-e4<-d1<-d2<-d3<-matrix(0,nz,4)
e1[env_lat==1]=1
e2[env_lat==2]=1
e3[env_lat==3]=1
e4[env_lat==4]=1
d1[diag_lat==1]=1
d2[diag_lat==2]=1
d3[diag_lat==3]=1
e1[is.na(env_lat)]=e2[is.na(env_lat)]=e3[is.na(env_lat)]=e4[is.na(env_lat)]=NA
d1[is.na(diag_lat)]=d2[is.na(diag_lat)]=d3[is.na(diag_lat)]=NA
```
Computing proportions of the different facies in the logs

```{r}
pe1 = mean(e1,na.rm=TRUE)
pe2 = mean(e2,na.rm=TRUE)
pe3 = mean(e3,na.rm=TRUE)
pe4 = mean(e4,na.rm=TRUE)
c(pe1,pe2,pe3,pe4)
pd1=mean(d1,na.rm=TRUE)
pd2=mean(d2,na.rm=TRUE)
pd3=mean(d3,na.rm=TRUE)
c(pd1,pd2,pd3)
pd1e1=mean(d1*e1,na.rm=TRUE)/pe1
pd1e2=mean(d1*e2,na.rm=TRUE)/pe2
pd1e3=mean(d1*e3,na.rm=TRUE)/pe3
pd1e4=mean(d1*e4,na.rm=TRUE)/pe4

@@

matrix(c(pd1e1,pd1e2,pd1e3,pd1e4,pd2e1,pd2e2,pd2e3,pd2e4,pd3e1,pd3e2,pd3e3,pd3e4),3,4,byrow=TRUE)
pe1+pe2+pe3+pe4
```
Building the grids for the Earth models

Because there are two fields: depositional and diagenetic, there are two grids

@@

```
displaying an image with all the logs
```{r}
# we are doubling the logs for a better visualization
im<-matrix(NA,100,91)
im[5,]<-env_lat[,1]
im[4,]<-env_lat[,1]
im[25,]<-env_lat[,2]
im[24,]<-env_lat[,2]
im[35,]<-env_lat[,3]
im[34,]<-env_lat[,3]
im[95,]<-env_lat[,4]
im[94,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
print image
```{r}
png(file="logslate.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
Another image the environment of depositions and the diagenesis logs
```{r}
im<-matrix(NA,100,91)
im[5,]<-diag_lat[,1]+4
im[4,]<-diag_lat[,1]+4
im[8,]<-env_lat[,1]
im[7,]<-env_lat[,1]
im[25,]<-diag_lat[,2]+4
im[24,]<-diag_lat[,2]+4
im[28,]<-env_lat[,2]
im[27,]<-env_lat[,2]
im[35,]<-diag_lat[,3]+4
im[34,]<-diag_lat[,3]+4
im[38,]<-env_lat[,3]
im[37,]<-env_lat[,3]
im[95,]<-diag_lat[,4]+4
im[94,]<-diag_lat[,4]+4
im[98,]<-env_lat[,4]
im[97,]<-env_lat[,4]
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),xlab="Lateral distance (m)",ylab="Vertical distance (m)")
```
print image
```{r}
png(file="logslatediag2.png",width=4000,height = 2500,res=300,antialias = )
image(x=(1:100)*9.2,y=(1:91)/10,z=im,col=c("lightgreen","dodgerblue4","darkmagenta","red","black","grey","yellow"),ylab="Vertical distance (m)",xlab = "Lateral distance (m)")
```

@@
